Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-17 prop_letter.tex
prop.bib Update citations...

We will start by reviewing IVPMs in the classical
setting~\cite{JamisonLodwick2004} and then propose our quantum
generalization. In the classical setting, there are several proposals
for ``imprecise
probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,PuriRalescu1983,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Teran2014,Grabisch2016}.''
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event $E$ is generalized from
a single real number to an interval of certainty $[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence for
the event and $r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

>>>>

We will start by reviewing IVPMs in the classical setting~\cite{JamisonLodwick2004}
and then propose our quantum generalization. In the classical setting,
there are several proposals for ``imprecise probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Grabisch2016}.''
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event $E$ is generalized
from a single real number to an interval of certainty $[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence
for the event and $r$ corresponds to the strength of evidence against
the event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.
